`r glue::glue('Initial inferCNV results for {params$library_id}')`

### 2025-04-17 analyses/infercnv-consensus-cell-type/template-notebooks/ewings-infercnv-results.Rmd
remove the scatterplot

* We used the `i3` HMM which has improved run times relative to the `i6` HMM.
* We used the default `analysis_mode = "subclusters"`, which allows the HMM to call CNVs at the level of clusters rather than whole samples or individual cells
* We used the following clustering parameters:
  * Leiden clustering run on PCA (not the expression matrix)
  * `k=20` nearest neighbors with a `resolution` parameter of 1 and using the `modularity` objective function

@@

## Compare references directly

We can also look at CNV predictions directly between references using a point-density scatterplot, with the Spearman correlation shown:

```{r, fig.height=6}
compare_refs <- has_cnv_df |>
  dplyr::filter(library_id == params$library_id) |>
  dplyr::select(
    barcodes, normal_reference, total_cnv_per_cell
  ) |>
  tidyr::pivot_wider(
    names_from = normal_reference,
    values_from = total_cnv_per_cell
  ) |>
  # color points this way rather than binning to ensure small bins aren't left out
  dplyr::add_count(`all-immune`, `subset-immune`)

# Determine max limit for axes
max_axis <- max(has_cnv_df$total_cnv_per_cell)
axis_breaks <- 1:max_axis

# Calculate in spearman correlation coefficient to include in plot
rho <- cor(compare_refs$`all-immune`, compare_refs$`subset-immune`, method = "spearman") |>
  round(2)

ggplot(compare_refs) +
  aes(
    x = `all-immune`,
    y = `subset-immune`,
    color = n
  ) +
  geom_point(size = 5) +
  geom_abline(color = "red") +
  scale_color_viridis_c() +
  coord_equal() +
  scale_x_continuous(limits = c(0, max_axis), breaks = 1:max_axis) +
  scale_y_continuous(limits = c(0, max_axis), breaks = 1:max_axis) +
  labs(
    title = "Per-cell CNVs between normal references",
    subtitle = glue::glue("rho = {rho}"),
    color = "Number of cells"
  ) +
  theme(legend.position = "bottom")
```

>>>>

* We used the `i6` HMM
* We used the default `analysis_mode = "subclusters"`, which allows the HMM to call CNVs at the level of clusters rather than whole samples or individual cells
* We used the following clustering parameters:
  * Leiden clustering run on PCA (not the expression matrix)
  * `k=20` nearest neighbors with a `resolution` parameter of 1 and using the `modularity` objective function

@@
